The paper on \Large \bf Blockchain Frontrunning

### 2018-09-07 frontrunning/Latex/sections/paper.tex
[frontrunning] On crypto-collectibles

% !TEX root = ../main.tex

\section{Introduction}

@@

\section{Preliminaries}

@@

%___________________________________________________________%

\section{Related Work}
As the traditional front-running was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something

@@

Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers. In order to get the required data, Ethereum blockchain data should be converted to a queryable format. For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}. Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}. A copy of this dataset and the findings can be found in \texttt{github.com / ANONYMOUS}.

@@

Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit. The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}

@@

\subsubsection{Miners}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.  For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token, i.e. TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction of 1000 TKN in the block he mines. Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to mine transactions in any order they prefer. However, miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, smart contract which adds all the participants to a party invite list, could only be closed by the smart contract owner. In this case when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

@@

%Some edits required here!

@@

\subsection{Crypto-Collectibles auctions} \hfill\\ 
Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain. Cryptokitties is known to be the most popular applications of ERC721 tokens~\cite{cryptokitties}. The main usage of these Cryptokitties is that users can breed them with each other and make new unique Cryptokitties, also they can buy or sell them through their main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{cryptokittie}.
To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract. This is similar to open auctions and everyone can see the bid value and what is the bid for, this transaction is visible from any other Ethereum node and could be easily front-run by sending the same transaction with higher gasPrice. 
%TODO: this needs a rewrite. 
% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40

@@

% Talk about how cryptokitties are similar to any other auctions .

@@

\section{How to stop Front-running?} %We have have the applicability of the solutions inline.

@@

\emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
%@shayan: ^

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible.

\subsection{Front-run Resistant Blockchain}
What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases). In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.

@@

@@

\subsubsection{Design Decision \#3: Loopring/Dual Authoring\newline}
Talk about this possible solution

@@

\subsection{Application Design to Prevent Front-running}

@@

\section{Concluding Remarks}

>>>>

% !TEX root = ../main.tex
%______________________________________________________________%
\section{Introduction}

@@

%______________________________________________________________%
\section{Preliminaries}

@@

%___________________________________________________________%
\section{Related Work}
As the traditional front-running was originated to trading financial instruments most of the literature are focused on financial aspects of the markets. %TODO: expand this with something

@@

Ethereum blockchain contains all transaction ever made on Ethereum, however, it is not easy to see the behaviour of the participants and miners solely using the default clients nor online blockchain explorers. In order to get the required data, Ethereum blockchain data should be converted to a queryable format. For this case study, we used open source projects such as Go Ethereum implementation\footnote{Official Go implementation of the Ethereum protocol\url{https://github.com/ethereum/go-ethereum}}, python script for extracting, transforming and loading ethereum blocks, named \texttt{ethereum-etl}~\cite{ethereumetl} and Google BigQuery\footnote{A fast, highly scalable, cost-effective, and fully managed cloud data warehouse for analytics \url{https://cloud.google.com/bigquery/}}. Using this software stack, we were able to query for all the transactions and blocks within the window of Status.im ICO for further analysis which was mainly done by data analysis tool \texttt{Tableau}\footnote{Tableau is a data visualization software that is used for data science and business intelligence.\url{https://www.tableau.com/}}. A copy of this dataset and the findings can be found in \texttt{github.com / ANONYMOUS}.

@@

Although this incident does not involve transaction reordering in the blocks, it shows how miners can modify their code to behave in a certain way to front-run other transactions and take advantage of the monetary profit. The dataset used for this analysis can be found on our GitHub repository.\footnote{Frontrunning Status.im ICO dataset: \url{http://github.com/TODO:ANONYMOUS}}. This analysis made us wonder, how many other DApps are vulnerable to front-running attack, who can front-run and what are the mitigation methods for decentral applications?

As the result of this analysis, we discovered a wide range of blockchain front-running case studies that are yet to investigated. Therefore, in the next sections we dive deeper into blockchain specific front-running details and analyze top recent DApps for front-running attack vectors and possible solutions proposed to mitigate these issues.

@@

\subsubsection{Miners}
Blockchain miners are the only parties who can decide on the order of transactions within a block they mine, they can easily intercept and reorder the transactions in their blocks, this is known as \textbf{transaction reordering} attack.  For example in an Ethereum based application, a miner learns about the pending \textit{buy} transaction of 1000 units of a token\ie TKN, presumably if this transaction goes through, it causes the price of the purchased token to increase. So the dishonest miner can step in front of this transaction and place his own buy order ahead. He would simply create his \textit{buy} of 1000 TKN and include it in front of the previous \textit{buy} transaction of 1000 TKN in the block he mines. Doing so, he would receive a better rate than other network users, and afterwards can sell the assets he has bought and gain a price advantage at the expense of others. Similarly, a dishonest miner can sell his tokens in front, if he sees a pending \textit{sell} transaction. In an open source blockchain application, there is no rules on how transactions must be ordered and miners are free to mine transactions in any order they prefer. However, miners can only front-run transactions within the blocks they happen to mine. They could do this also by not broadcasting their own transactions to the network, this makes the miners to be less noticeable to the network when front-running.
Another example here is in the case of decentral exchanges and order cancellation. Every exchange should have the functionality to cancel the orders, especially for a volatile market. In this case, when user decides that her order is not profitable anymore, she would send a cancelation transaction. Here the miner sees the cancelation transaction and puts his own order in front of the cancellation transaction --transaction reordering-- to fill the order, potentially profiting from the order. They can also include the canceled transaction in their block to collect the full gas limit used by that transaction~\cite{CostofDecentralization:online}, see Figure~\ref{MinerFrontrunning}. Front-running can also occur in non-financial smart contracts. As an example, smart contract which adds all the participants to a party invite list, could only be closed by the smart contract owner. In this case when the owner sends the transaction to close the list, a miner can include his own list of participants before the close transaction in the block he mines. This is an issue with the design of the smart contracts and is known as transaction-ordering dependence vulnerability~\cite{luu2016making}.

@@

%Some edits required here! @mahsa TODO

@@

%______________________________________________________________%
\subsection{Crypto-Collectibles Games} \hfill\\

%TODO: shayan: connect games to cryptokitties and other collectibles

Crypto-Collectibles, also known as ERC-721 Non-Fungible Token Standard~\cite{erc721}, are one of the applications of Ethereum blockchain. Cryptokitties is known to be one of the first and the most popular use cases of ERC721 tokens~\cite{cryptokitties}. Their marketcap reached more than 6 million dollars in the first months their launch. Crypto-Collectibles, are similar to ERC-20 tokens and can be listed on exchanges. Most of the front-running issues applied to the exchanges also apply to DApps using ERC-721 tokens. \\

As an example Cryptokitties can be bred, bought or sold through the main interface\footnote{Cryptokitties website \url{https://www.cryptokitties.co/}}. See Figure~\ref{cryptokittie}.
To buy a cryptokittie, user sends a bid transaction \textit{bid(uint256 \_tokenId)} containing the cryptokittties ID which can be found either on their website or on the ERC721 token smart contract. This is similar to open auctions, bid value and the object bidding on is visible to the network and any user could be easily front-run by sending the same transaction with higher gasPrice to replace the initial bidder. 
% https://etherscan.io/tx/0x62a76b7e345e8abd463487d0348c118a9314b197024e090fee7b1fbce434da40

@@

@@

%TODO: Shayan: Frontrunning on one of the gambling DAPPS from the table

%______________________________________________________________%
\section{How to stop Front-running?} %We have have the applicability of the solutions inline.

@@

\emph{Traditional Front-running Prevention Methods}. regulations/enforcement/broker education/sealed order
%@shayan: ^ TODO!

@@

There are two main approaches to prevent front running, one to design a blockchain that is front-run resistant , and the other to design the application logics in a way that front running is not possible. 
%@shayan: ^ TODO!

%______________________________________________________________%
\subsection{Front-run Resistant Blockchain}
What does this mean to have a front-run resistant blockchain?  There are technical difficulties to achieve such solutions as there are unknown factors within such network designs (corner/edge cases). In this section, we describe the potential solutions using which, one can design and implement a decentral application that is resistant to front-running.

@@

%@shayan TODO

@@

\subsubsection{Design Decision \#3: Loopring/Dual Authoring\newline}
Talk about this possible solution
%MAHSA TODO
%https://medium.com/loopring-protocol/dual-authoring-looprings-solution-to-front-running-d0fc9c348ef1
% https://raw.githubusercontent.com/Loopring/whitepaper/master/en_whitepaper.pdf

@@

%______________________________________________________________%
\subsection{Application Design to Prevent Front-running}

@@

%______________________________________________________________%
\section{Concluding Remarks}
